\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-06-08 short.tex
only slightly longer than two pages

Much of everyday human thinking and learning can be understood in
terms of program induction: constructing a procedure that maps inputs
to desired outputs, based on observing example input-output pairs.
People can induce programs flexibly across many different domains, often from just one or a few examples.  For instance, if
shown that a text-editing program should map ``Jane Morris Goodall''
to ``J. M. Goodall'', we can guess it maps ``Richard Erskine Leakey''
to ``R. E. Leakey''; if instead the first input mapped to
``Dr. Jane'' or ``Goodall, Jane'', we might guess
the latter should map to ``Dr. Richard'' or ``Leakey, Richard'',
 respectively.

The FlashFill system~\cite{gulwani2011automating} embedded in
Microsoft Excel solves problems such as these and is probably the best
known practical program-induction algorithm, but researchers in
programming languages and AI have had successes in many domains, such as handwriting recognition and
generation~\cite{lake2015human}, procedural
graphics~\cite{ellis2017learning}, question
answering~\cite{johnson2017clevr} and robot motion
planning~\cite{devlin2017neural}.  These systems
work in different ways, but most hinge upon a carefully engineered
\textbf{Domain Specific Language (DSL)}.  This is especially true for
systems like FlashFill that induce a wide range of programs
very quickly, in a few seconds or less.  DSLs constrain the search
over programs with strong prior knowledge in the form of a restricted
set of programming primitives finely tuned to the domain: for
text editing, these are operations like appending and
splitting on characters.

In this work, we consider the problem of building agents that learn to solve
program induction tasks, and also the problem of acquiring the prior knowledge
necessary to quickly solve these tasks in a new domain.  Representative problems
in three domains are shown in Table~\ref{initialExampleDSL}.  Our solution is an
algorithm that grows or boostraps a DSL while jointly training a neural network
to help write programs in the increasingly rich DSL.
%
% (JBT: MAYBE INSERT FIGURE FROM ICML PAPER?)
%
\begin{table*} %[t!]
  \makebox[\textwidth][c]{
    \scriptsize
  \tabcolsep=4pt
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{>{\hspace{-0em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-2.5em}}c<{\hspace{-0.8em}}>{\hspace{-1em}}c<{\hspace{-1em}}}
    \toprule
    &{\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
    \rotatebox[origin=c]{90}{\normalsize \pop{Programs} \& Tasks}&{\tabcolsep=7pt
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 2\, 3]}$\to $\code{[7\, 3]}         \\
          \code{[1\, 2\, 3\, 4]}$\to $\code{[3\, 4]} \\
          \code{[4\, 3\, 2\, 1]}$\to $\code{[4\, 3]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ ($\lambda$ (x)}}\\
          \hspace{1.15cm}\pop{\code{(> x 2)))}}       \\
          \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    }
    &
    \hspace{-0.5cm}\begin{tabular}{c}
      +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
      +83 973-831$\to $83.973.831\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{-}
      }}\\
      \hspace{1.25cm}\pop{\code{($f_0$ \codechar{.} \codechar{ }}}\\
      \hspace{1.4cm}\pop{\code{(cdr s)))}}\\
      ~\\
      Temple Anna H $\to $TAH\\
      Lara Gregori$\to $LG\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}}\\
    \end{tabular}
    &
    \begin{tabular}{cc}
      \includegraphics[width = 3em]{figures/functions/4.png}&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \pop{\code{$f($x$) = $($f_1$ x)}}&    \pop{\code{$f($x$) = $($f_6$ x)}}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \pop{\code{$f($x$) = $($f_4$ x)}}&    \pop{\code{$f($x$) = $($f_3$ x)}}\\

@@

%% Our \system
%% algorithm incorporates these insights by iterating
Concretely, our algorithm iterates through three cycles:
\\\noindent\textbf{Wake Cycle}: Here we take a given set of \textbf{tasks}, typically
several hundred, and search for compact programs that solve these tasks.
Our current implementation uses a simple and generic enumerative program synthesis algorithm,
enumerating programs written in the current DSL in order of their probability according to the neural network.
\\\noindent\textbf{Sleep-G Cycle}: Here we grow the the DSL (or \textbf{G}enerative model),
which allows the agent to more compactly
write programs in the domain. We modify the structure of the DSL by
discovering regularities across programs found during waking, compressing
them to distill out common code fragments across successful programs.
The technical machinery behind this DSL learning
comes from a formalism known as Fragment Grammars~\cite{tim},
which casts DSL induction as grammar induction.
\\\noindent\textbf{Sleep-R Cycle}: Here we improve the search procedure by training a neural network (the \textbf{R}ecognition model) to
predict a distribution over programs written in the current DSL, in the spirit of ``amortized'' or
``compiled'' inference~\cite{le2016inference}.
The recognition model is trained, conditioned on a task, to assign high probability to
programs that (1) have high prior probability according to the current DSL,
while (2) also assigning high likelihood to the task at hand,
thus amortizing the cost of finding programs with high posterior probability.

@@

\subsection{Programs that manipulate sequences}\label{sequences}
We apply \system to list processing %% (Section~\ref{listSection})
and text editing, %% (Section~\ref{textSection})
using a GRU~\cite{cho2014learning} for
the recognition model, and initially providing the system with generic sequence manipulation primitives:
\code{foldr}, \code{unfold}, \code{if}, \code{map}, \code{length},
\code{index}, \code{=}, \code{+}, \code{-}, \code{0}, \code{1}, \code{cons},
\code{car}, \code{cdr}, \code{nil}, and \code{is-nil}.

%\subsubsection{List Processing}\label{listSection}
\textbf{List Processing:} Synthesizing programs that manipulate data structures is a widely studied
problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of learning functions that
manipulate lists, and also perform arithmetic operations upon lists (Table~\ref{listExamples}).
We created 236 human-interpretable list manipulation tasks, each with 15
input/output examples.
%% Our data set is interesting in three major ways: many of the tasks
%% require complex solutions; the tasks were not generated from some
%% latent DSL, and the agent must learn to solve these complicated
%% problems from only 236 tasks.
%% Our data set assumes arithmetic operations as well as sequence operations,
%% so we additionally provide our system with the following arithmetic
%% primitives: \code{mod}, \code{*}, \code{>}, \code{is-square},
%% \code{is-prime}.
%% evaluating  on a 50/50 test/train split.
In solving these tasks, the system
composed 38 new subroutines, and rediscovered the higher-order
function \code{filter} ($f_1$ in Table~\ref{initialExampleDSL}, left).%% , yielding a more expressive DSL more closely
%% matching the domain (Tbl.~\ref{initialExampleDSL}, left).
%% \begin{figure}[b]\centering
%% \vspace{-0.5cm}  \begin{tabular}{lll}
%%     \toprule
%%     Name & Input & Output \\\midrule
%%     repeat-3 & [7\, 0] & [7\, 0\, 7\, 0\, 7\, 0] \\
%% %    drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
%%     rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
%% %    count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
%%     keep-div-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
%%     product & [7\, 1\, 6\, 2] & 84 \\
%%     \bottomrule
%%   \end{tabular}
%%   \captionof{table}{Some tasks in our list function domain.}\label{listExamples}\vspace{-0.5cm}
%% \end{figure}

@@

We trained our system on 109 automatically-generated text editing tasks, with 4 input/output examples each.
After three iterations, it assembles a DSL containing a dozen new functions (Fig.~\ref{initialExampleDSL}, center) solving
all the training tasks.
But, how well does the  learned DSL generalized to real text-editing scenarios?
We tested, but did not train, on the 108 text editing problems from the SyGuS~\cite{alur2016sygus} program synthesis competition. Before any learning,
\system solves 3.7\% of the problems with an average search time of 235 seconds.
After learning,
it solves 74.1\%, and does so much faster,
solving them in an average of 29 seconds.
As of the 2017 SyGuS competition,
the best-performing algorithm solves 79.6\% of the problems.
But, SyGuS comes with a
different hand-engineered DSL \emph{for each text editing problem}. %\footnote{SyGuS text editing problems also prespecify the set of allowed string constants for each task. For these experiments, our system did not use this assistance.}
Here  we learned a single DSL
that applied generically to
all of the tasks,
and perform comparably to the best
prior work.

\subsection{Symbolic Regression: Programs from visual input}\label{regressionSection}
We apply \system
to symbolic regression problems.  Here, the
agent observes points along the curve of a function, and must write a
program that fits those points.  We initially equip our learner with
addition, multiplication, and division, and task it with solving
100 %% symbolic regression
problems, each either a polynomial or rational function.  The recognition model is a
convnet that observes an image of the target function's
graph (Fig.~\ref{functions}) --- visually, different kinds of
polynomials and rational functions produce different kinds of graphs,
and so the convnet can  look at a graph and predict
what kind of function best explains it.
These programs can contain real numbers,
which we set with gradient descent,
and penalize continuous parameters by
incorporating a BIC penalty into the likelihood model $\probability[x|p]$.
%% A key difficulty, however, is
%% that these problems are best solved with programs containing real
%% numbers.  Our solution to this difficulty is to enumerate
%%  programs with real-valued parameters, and then fit those
%% parameters by automatically differentiating through the programs the
%% system writes and use gradient descent to fit the parameters.
%% We define the likelihood model, $\probability[x|p]$, by assuming a Gaussian noise model for the input/output examples,
%% and penalize the use of real-valued parameters using the BIC~\cite{Bishop:2006:PRM:1162264}.
\begin{figure}\vspace{-0.0cm} \newcommand{\functionSize}{1.1cm}\centering
  \begin{minipage}[c]{0.3\columnwidth}%\vspace{-0.3cm}
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/48.png}\\
  \includegraphics[width = \functionSize]{figures/functions/102.png}
  \includegraphics[width = \functionSize]{figures/functions/116.png}\\
  \vspace{1pt}%\includegraphics[width = \functionSize]{figures/functions/181.png}
  %\includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
    \includegraphics[width = \functionSize]{figures/functions/149.png}
  \end{minipage}
  \begin{minipage}[c]{0.69\columnwidth}    
    \caption{Recognition model input for symbolic regression. DSL learns subroutines for polynomials (top rows) and rational functions (bottom) while the recognition  model jointly learns to look at a graph of the function (left) and predict which learned subroutines best explain the observation.}\label{functions}\vspace{-1cm}
        \end{minipage}
\end{figure}
We learn a DSL containing 13 new functions,
mainly templates for polynomials of different orders or ratios of polynomials.
The model also learns to find programs minimizing the number of continuous parameters ---
learning to represent linear functions with 
\code{(* real (+ x real))}, which has two continuous parameters, and represents quartic functions using $f_4$ in the rightmost column of Fig.~\ref{initialExampleDSL}
which has five continuous parameters.
This phenomenon arises from our Bayesian framing.

\subsection{Quantitative Results on Held-Out Tasks}\label{quantitative}
We evaluate  on held-out testing tasks,
measuring how many
tasks are solved and how long it takes to solve them (Fig.~\ref{learningCurves}).
Prior to any learning,
the system cannot find solutions for most of the tasks,
and those it does solve take a long time;
with more wake/sleep iterations,
we converge upon DSLs and recognition models 
more closely matching the domain.

@@

\begin{figure*}\centering
  \includegraphics[width = 4.5cm]{figures/listLearningCurve.eps} \qquad
  \includegraphics[width = 4.5cm]{figures/textLearningCurve.eps}\qquad
  \includegraphics[width = 4.5cm]{figures/rationalCurve.eps}
\vspace{-0.4cm}  \caption{Learning curves for \system both with (\orange{in orange}) and without
    (\teal{in teal}) the recognition model. Solid lines: \% holdout testing tasks solved w/ 10m timeout. Dashed lines: Average solve time, averaged only over tasks that are solved.}\label{learningCurves}\vspace{-0.5cm}
\end{figure*}

>>>>

%% Much of everyday human thinking and learning can be understood in
%% terms of program induction: constructing a procedure that maps inputs
%% to desired outputs, based on observing example input-output pairs.
Humans can induce programs flexibly across many different domains, often from just one or a few examples.  If
shown that a text-editing program should map ``Jane Morris Goodall''
to ``J. M. Goodall'', we can guess it maps ``Richard Erskine Leakey''
to ``R. E. Leakey''; if the first input mapped to
``Dr. Jane'' or ``Goodall, Jane'', we might guess
the latter mapped to ``Dr. Richard'' or ``Leakey, Richard'',
 respectively.

The FlashFill system~\cite{gulwani2011automating} embedded in
Microsoft Excel solves problems such as these and is probably the best
known practical program-induction algorithm, but researchers in
programming languages and AI have had successes in many domains, such as handwriting recognition and
generation~\cite{lake2015human}, question
answering~\cite{johnson2017clevr} and robot motion
planning~\cite{devlin2017neural}.  These systems
work in different ways, but most hinge upon a carefully engineered
\textbf{Domain Specific Language (DSL)}.  %% This is especially true for
%% systems like FlashFill that induce a wide range of programs
%% very quickly, in a few seconds or less.  
DSLs constrain the search
over programs with strong prior knowledge in the form of a restricted
library of primitives tuned to the domain: for
text editing, these are operations like appending and
splitting on strings.

In this work, we consider the problem of building agents that learn to solve
program induction tasks, and also the problem of acquiring the prior knowledge
necessary to quickly solve these tasks in a new domain; see
 Table~\ref{initialExampleDSL}.  Our solution is an
algorithm that grows or boostraps a DSL while jointly training a neural network
to help write programs in the increasingly rich DSL.
%
% (JBT: MAYBE INSERT FIGURE FROM ICML PAPER?)
%
\begin{table*} %[t!]
  \makebox[\textwidth][c]{
    \scriptsize
  \tabcolsep=4pt
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{>{\hspace{-0em}}c<{\hspace{-1em}}>{\hspace{-1em}}c<{\hspace{-1em}}>{\hspace{-2.5em}}c<{\hspace{-0.8em}}>{\hspace{-1em}}c<{\hspace{-1em}}}
    \toprule
    &{\normalsize List Functions}&{\normalsize Text Editing}&{\normalsize Symbolic Regression}\\\midrule
    \rotatebox[origin=c]{90}{\normalsize \pop{Programs} \& Tasks}&{\tabcolsep=7pt
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 2\, 3]}$\to $\code{[7\, 3]}         \\
          \code{[1\, 2\, 3\, 4]}$\to $\code{[3\, 4]} \\
          \code{[4\, 3\, 2\, 1]}$\to $\code{[4\, 3]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ ($\lambda$ (x)}}\\
          \hspace{1.15cm}\pop{\code{(> x 2)))}}       \\
          \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    }
    &
    \hspace{-0.5cm}\begin{tabular}{c}
      +106 769-438$\to $106.769.438\\%&Nancy FreeHafer $\longrightarrow$ Dr. Nancy\\
      +83 973-831$\to $83.973.831\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_0$\code{  \codechar{.} \codechar{-}
      }}\\
      \hspace{1.25cm}\pop{\code{($f_0$ \codechar{.} \codechar{ }}}\\
      \hspace{1.4cm}\pop{\code{(cdr s)))}}\\
      ~\\
      Temple Anna H $\to $TAH\\
      Lara Gregori$\to $LG\\
      \pop{$f(\text{\code{s}}) = $\code{(}$f_2$\code{ s)}}\\
    \end{tabular}
    &
    \begin{tabular}{cc}
      \includegraphics[width = 3em]{figures/functions/4.png}&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \pop{\code{$f($x$) = $($f_1$ x)}}&    \pop{\code{$f($x$) = $($f_6$ x)}}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \pop{\code{$f($x$) = $($f_4$ x)}}&    \pop{\code{$f($x$) = $($f_3$ x)}}\\

@@

%% Our \system
%% algorithm incorporates these insights by iterating
Concretely, our algorithm iterates through three cycles:
\\\noindent\textbf{Wake Cycle}: Given a set of \textbf{tasks}, typically
several hundred, we search for compact programs that solve these tasks.
Currently we take the simple strategy of
enumerating programs written in the current DSL in order of their probability according to the neural network.
\\\noindent\textbf{Sleep-G Cycle}: Here we grow the the DSL (or \textbf{G}enerative model),
which allows the agent to more compactly
write programs in the domain. We modify the structure of the DSL by
discovering regularities across programs found during waking, compressing
them to distill out common code fragments across successful programs.
The technical machinery behind this DSL learning
comes from a formalism known as Fragment Grammars~\cite{tim},
which casts DSL induction as grammar induction.
\\\noindent\textbf{Sleep-R Cycle}: This trains a neural net (the \textbf{R}ecognition model) to
predict a distribution over programs written in the current DSL, in the spirit of ``amortized'' or
``compiled'' inference~\cite{le2016inference}.
The network is trained, conditioned on a task, to assign high probability to
programs that have high prior probability according to the current DSL,
while also assigning high likelihood to the task at hand,
thus amortizing the cost of finding programs with high posterior probability.

@@

We apply \system to list processing %% (Section~\ref{listSection})
and text editing, %% (Section~\ref{textSection})
using a recurrent network for
the recognition model, and initially providing the system with generic sequence manipulation primitives:
\code{foldr}, \code{unfold}, \code{if}, \code{map}, \code{length},
\code{index}, \code{=}, \code{+}, \code{-}, \code{0}, \code{1}, \code{cons},
\code{car}, \code{cdr}, \code{nil}, and \code{is-nil}.

%\subsubsection{List Processing}\label{listSection}
\textbf{List Processing:} Synthesizing programs that manipulate data structures is a widely studied
problem in the programming languages community~\cite{feser2015synthesizing}.
%with applications to computer aided programming~\cite{solar2008program}.
We consider this problem within the context of learning functions that
manipulate lists,
creating 236 human-interpretable list manipulation tasks (Table~\ref{initialExampleDSL}, left).
%% Our data set is interesting in three major ways: many of the tasks
%% require complex solutions; the tasks were not generated from some
%% latent DSL, and the agent must learn to solve these complicated
%% problems from only 236 tasks.
%% Our data set assumes arithmetic operations as well as sequence operations,
%% so we additionally provide our system with the following arithmetic
%% primitives: \code{mod}, \code{*}, \code{>}, \code{is-square},
%% \code{is-prime}.
%% evaluating  on a 50/50 test/train split.
In solving these tasks, the system
composed 38 new subroutines, and rediscovered the higher-order
function \code{filter} ($f_1$ in Table~\ref{initialExampleDSL}, left).%% , yielding a more expressive DSL more closely
%% matching the domain (Tbl.~\ref{initialExampleDSL}, left).
%% \begin{figure}[b]\centering
%% \vspace{-0.5cm}  \begin{tabular}{lll}
%%     \toprule
%%     Name & Input & Output \\\midrule
%%     repeat-3 & [7\, 0] & [7\, 0\, 7\, 0\, 7\, 0] \\
%% %    drop-3 & [0\, 3\, 8\, 6\, 4] & [6\, 4] \\
%%     rotate-2 & [8\, 14\, 1\, 9] & [1\, 9\, 8\, 14] \\
%% %    count-head-in-tail & [1\, 2\, 1\, 1\, 3] & 2 \\
%%     keep-div-5 & [5\, 9\, 14\, 6\, 3\, 0] & [5\, 0] \\
%%     product & [7\, 1\, 6\, 2] & 84 \\
%%     \bottomrule
%%   \end{tabular}
%%   \captionof{table}{Some tasks in our list function domain.}\label{listExamples}\vspace{-0.5cm}
%% \end{figure}

@@

We trained our system on 109 automatically-generated text editing tasks.
After three wake/sleep cycles, it assembles a DSL containing a dozen new functions (Fig.~\ref{initialExampleDSL}, center) solving
the training tasks.
%But, how well does the  learned DSL generalized to real text-editing scenarios?
We also tested, but did not train, on the 108 text editing problems from the SyGuS~\cite{alur2016sygus} program synthesis competition. Before any learning,
\system solves 3.7\% of the problems with an average search time of 235 seconds.
After learning,
it solves 74.1\%, and does so much faster,
solving them in an average of 29 seconds.
As of the 2017 SyGuS competition,
the best-performing algorithm solves 79.6\% of the problems.
But, SyGuS comes with a
different hand-engineered DSL \emph{for each text editing problem}. %\footnote{SyGuS text editing problems also prespecify the set of allowed string constants for each task. For these experiments, our system did not use this assistance.}
Here  we learned a single DSL
that applied generically to
all of the tasks,
and perform comparably to the best
prior work.

\textbf{Symbolic Regression: Programs from visual input.}
We apply \system
to symbolic regression problems.  Here, the
agent observes points along the curve of a function, and must write a
program that fits those points.  We initially equip our learner with
addition, multiplication, and division, and task it with solving
100 %% symbolic regression
problems, each either a polynomial or rational function.  The recognition model is a
convnet that observes an image of the target function's
graph (Fig.~\ref{functions}) --- visually, different kinds of
polynomials and rational functions produce different kinds of graphs,
and so the convnet can  look at a graph and predict
what kind of function best explains it.
%% These programs can contain real numbers,
%% which we set with gradient descent,
%% and penalize continuous parameters by
%% incorporating a BIC penalty into the likelihood model $\probability[x|p]$.
%% A key difficulty, however, is
%% that these problems are best solved with programs containing real
%% numbers.  Our solution to this difficulty is to enumerate
%%  programs with real-valued parameters, and then fit those
%% parameters by automatically differentiating through the programs the
%% system writes and use gradient descent to fit the parameters.
%% We define the likelihood model, $\probability[x|p]$, by assuming a Gaussian noise model for the input/output examples,
%% and penalize the use of real-valued parameters using the BIC~\cite{Bishop:2006:PRM:1162264}.
\begin{figure}\vspace{-0.0cm} \newcommand{\functionSize}{1.1cm}\centering
  \begin{minipage}[c]{0.3\columnwidth}%\vspace{-0.3cm}
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/48.png}\\
  \includegraphics[width = \functionSize]{figures/functions/102.png}
  \includegraphics[width = \functionSize]{figures/functions/116.png}\\
  \vspace{1pt}%\includegraphics[width = \functionSize]{figures/functions/181.png}
  %\includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
    \includegraphics[width = \functionSize]{figures/functions/149.png}
  \end{minipage}
  \begin{minipage}[c]{0.69\columnwidth}    
    \caption{Recognition model input for symbolic regression. DSL learns subroutines for polynomials (top rows) and rational functions (bottom) while the recognition  model jointly learns to look at a graph of the function (left) and predict which learned subroutines best explain the observation.}\label{functions}\vspace{-1cm}
        \end{minipage}
\end{figure}
%% We learn a DSL containing 13 new functions,
%% mainly templates for polynomials of different orders or ratios of polynomials.
%% The model also learns to find programs minimizing the number of continuous parameters ---
%% learning to represent linear functions with 
%% \code{(* real (+ x real))}, which has two continuous parameters, and represents quartic functions using $f_4$ in the rightmost column of Fig.~\ref{initialExampleDSL}
%% which has five continuous parameters.
%% This phenomenon arises from our Bayesian framing.

%% \subsection{Quantitative Results on Held-Out Tasks}\label{quantitative}
%% We evaluate  on held-out testing tasks,
%% measuring how many
%% tasks are solved and how long it takes to solve them (Fig.~\ref{learningCurves}).
%% Prior to any learning,
%% the system cannot find solutions for most of the tasks,
%% and those it does solve take a long time;
%% with more wake/sleep iterations,
%% we converge upon DSLs and recognition models 
%% more closely matching the domain.

@@

\begin{figure*}\centering
  \includegraphics[width = 4.5cm]{figures/listLearningCurve.eps} \qquad
  \includegraphics[width = 4.5cm]{figures/textLearningCurve.eps}\qquad
  \includegraphics[width = 4.5cm]{figures/rationalCurve.eps}
\vspace{-0.4cm}  \caption{Learning curves for \system both with (\orange{in orange}) and without
    (\teal{in teal}) the recognition model. Iterations: \# wake/sleep cycles. Solid lines: \% holdout testing tasks solved w/ 10m timeout. Dashed lines: Average solve time.}\label{learningCurves}\vspace{-0.5cm}
\end{figure*}
